PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 1$

### 2014-07-15 qfenv_paper/qf_environment.tex
Changes to QF section
Included preliminary (and poorly written) discussion.

\section{Stellar Mass Function} \label{sec:smf}
The target galaxy sample defined above has so far been classified into quiescent or star-forming and low or high density environments. We further divide these subsamples into bins of redshift: $0.0375-0.145$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ for a total 16 subsamples. In this section, we calculate the SMF for each of these 16 subsamples.

To calculate the SMFs we employ a non-parametric $1/{V_{\rm{max}}}$ estimator commonly used for galaxy luminosity functions and stellar mass functions, as done in \cite{Moustakas:2013aa} and discussed in the review \cite{Johnston:2011aa}. The differential SMF is given by the following equation:
\begin{equation} \label{eq:phi}
\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log} \:\mathcal{M}) = \sum\limits_{i=1}^{N} \frac{w_i}{V_{\rm{max,avail},i}}. 
\end{equation}
The equation above is same as Equation 3. in \cite{Moustakas:2013aa} except for $V_{\rm{max,avail}}$ instead than $V_{\rm{max}}$, to account for the edge effects of the survey discussed in Section \ref{sec:edgeeffect}. $w_i$ is the statistical weight of galaxy $i$ and $\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log}\: \mathcal{M})$ is the number of galaxies ($N$) per unit volume within the stellar mass range $[\rm{log} \:\mathcal{M}, \rm{log} \:\mathcal{M}+\Delta(\rm{log} \:\mathcal{M})]$.

@@

To calculate $V_{\rm{max,avail},i}$, we generate a sample of points with random $RA$, $Dec$ within the window function of our galaxy sample (SDSS-{\em GALEX} window function and the five PRIMUS fields) and random $z$ within the redshift range. This is not to be confused with the \texttt{ransack} sample in Section \ref{sec:edgeeffect}. We then impose the same edge effect cutoffs we applied to our galaxy sample, using the same \texttt{ransack} environment calculation method from above. At redshift bins of $\Delta z \sim 0.01$, we compute the fraction of random points that remain in the bin after the edge effect cutoffs: $f_{\rm{edge}}$. We then apply this factor to compute $V_{\rm{max,avail}} = V_{\rm{max}} \times f_{\rm{edge}}$. The $V_{\rm{max}}$ in the equation above are computed following the method described in \cite{Moustakas:2013aa} Section 4.2 with the same redshift-dependent $K$-correction from observed SED and luminosity evolution model.

In order to calculate the uncertainty of the SMFs from the sample variance, we use a standard jackknife technique (as done in \cite{Moustakas:2013aa}). For the PRIMUS galaxies, we calculate SMFs after excluding one of the five target fields at a time. For the SDSS target galaxies we divide the field into a 12 $\times$ 9 rectangular $RA$ and $Dec$ grid and calculate the SMFs after excluding one grid each time. Then using the calculated SMFs we calculate the uncertainty: 
\begin{equation}
\sigma^j = \sqrt{\frac{M-1}{M} \sum\limits_{k=1}^{M} (\Phi^j_k - \langle \Phi^j \rangle)^2}
\end{equation} 
$M$ in this equation is the number of jack knife SMFs in the stellar mass bin. $\langle \Phi^j \rangle$ is the mean number density of galaxies 
in each stellar mass bin for all of the jack knife $\Phi^j$s.

@@

\section{Quiescent Fraction} \label{sec:qf_const}
The SMFs calculated in the previous section describe the stellar mass distribution of our galaxy population and reveal the evolution of this distribution over comic time. We compare the quiescent and the star-forming populations, using the SMFs, in order to quantify the fraction of galaxies that have depleted their star-formation - the quiescent fraction. Adding environment classifications to our analysis, we investigate the effects of environment on the quiescent fraction and its evolution. By comparing the quiescent fraction evolution between high and low environments we are able to isolate and quantify the effects of environment dependent external quenching mechanisms as opposed to the internal mechanisms that operate within the galaxy.

@@

In both panels, $f_{\rm{Q}}$ increases monotonically as a function of mass for all redshift bins. This result is strongly consistent with the well established trend that generally more massive galaxies are more likely to be quenched. Furthermore, the results are also consistent with previous measurements of the quiescent fraction. Using a group-finding algorithm on the SDSS DR7 catalog, \cite{Tinker:2011aa} presented the relationship between $f_{\rm{Q}}$ and overdensity for galaxies within the mass range $\rm{log} \; \mathcal{M}_{*} = [9.8, 10.1]$. The \cite{Tinker:2011aa} $f_{\rm{Q}}$ values at the lowest and highest overdensity values, $f_{\rm{Q}} \sim 0.4$ and $f_{\rm{Q}} \sim 0.6$ respectively, are consistent with our SDSS sample low and high density environment $f_{\rm{Q}}$ at the lowest mass bin $\rm{log} \; \mathcal{M} \sim 10.2$. Likewise at higher redshifts, our high and low environment $f_{\rm{Q}}$ results are in general agreement with the $F_{\rm{blue}}$ values for group and isolated galaxies from the zCOSMOS Redshift Survey, as presented in \cite{Iovino:2010aa}.

@@

In addition to its relation with mass, in Figure \ref{fig:qf}, $f_{\rm{Q}}$ increases as redshift decreases for all masses and environments. Though restricted by the stellar mass limits, the $f_{\rm{Q}}$ evolution exhibits a slight mass dependence. $f_{\rm{Q}}$ in low density environments shows a greater evolution between redshift bins at high masses than at low masses. In contrast, the $f_{\rm{Q}}$ in high density environments shows a greater evolution between redshift bins at low masses than at high masses.

>>>>

\section{Stellar Mass Function} \label{sec:smf}
The target galaxy sample defined above has so far been classified into quiescent or star-forming and low or high density environments. We further divide these subsamples into redshift bins: $0.0375-0.145$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ for a total 16 subsamples. In this section, we calculate the SMF for each of these subsamples.

To calculate the SMFs we employ a non-parametric $1/{V_{\rm{max}}}$ estimator commonly used for galaxy luminosity functions and stellar mass functions, as done in \cite{Moustakas:2013aa} and discussed in the review \cite{Johnston:2011aa}. The differential SMF is given by the following equation:
\begin{equation} \label{eq:phi}
\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log} \:\mathcal{M}) = \sum\limits_{i=1}^{N} \frac{w_i}{V_{\rm{max,avail},i}}. 
\end{equation}
The equation above is same as Equation 3. in \cite{Moustakas:2013aa} except that we use $V_{\rm{max,avail}}$ instead than $V_{\rm{max}}$, to account for the edge effects of the survey discussed in Section \ref{sec:edgeeffect}. $w_i$ is the statistical weight of galaxy $i$ and $\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log}\: \mathcal{M})$ is the number of galaxies ($N$) per unit volume within the stellar mass range $[\rm{log} \:\mathcal{M}, \rm{log} \:\mathcal{M}+\Delta(\rm{log} \:\mathcal{M})]$.

@@

To calculate $V_{\rm{max,avail},i}$, we generate a sample of points with random $RA$, $Dec$ within the window function of our galaxy sample (SDSS-{\em GALEX} window function and the five PRIMUS fields) and random $z$ within the redshift range. This is not to be confused with the \texttt{ransack} sample in Section \ref{sec:edgeeffect}. We then impose the same edge effect cutoffs we applied to our galaxy sample, using the same \texttt{ransack} environment calculation method, also discuseed in Section \ref{sec:edgeeffect}. At redshift bins of $\Delta z \sim 0.01$, we compute the fraction of random points that remain in the bin after the edge effect cutoffs: $f_{\rm{edge}}$. We then apply this factor to compute $V_{\rm{max,avail}} = V_{\rm{max}} \times f_{\rm{edge}}$. The $V_{\rm{max}}$ in the equation above are computed following the method described in \cite{Moustakas:2013aa} Section 4.2 with the same redshift-dependent $K$-correction from observed SED and luminosity evolution model.

In order to calculate the uncertainty of the SMFs from the sample variance, we use a standard jackknife technique (as done in \cite{Moustakas:2013aa}). For the PRIMUS galaxies, we calculate SMFs after excluding one of the five target fields at a time. For the SDSS target galaxies we divide the field into a 12 $\times$ 9 rectangular $RA$ and $Dec$ grid and calculate the SMFs after excluding one grid each time. Using the calculated SMFs we calculate the uncertainty: 
\begin{equation}
\sigma^j = \sqrt{\frac{M-1}{M} \sum\limits_{k=1}^{M} (\Phi^j_k - \langle \Phi^j \rangle)^2}
\end{equation} 
$M$ in this equation is the number of jack knife SMFs in the stellar mass bin. $\langle \Phi^j \rangle$ is the mean number density of galaxies 
in each stellar mass bin for all of the jack knife $\Phi^j$s.

@@

\section{Quiescent Fraction} \label{sec:qf_const}
The SMFs calculated in the previous section describe the stellar mass distribution of our galaxy population and reveal the evolution of this distribution over comic time. We compare the quiescent and the star-forming populations, using the SMFs, and quantify the fraction of galaxies that have depleted their star-formation - the quiescent fraction. Adding environment classification to our analysis, we investigate the effects of environment on the quiescent fraction and its evolution. By comparing the evolution between high and low environments we are able to isolate and quantify the effects of environment dependent external quenching mechanisms as opposed to the internal mechanisms that operate within the galaxy.

@@

In both panels, the $f_{\rm{Q}}$s reveal a clear mass dependence where $f_{\mr{Q}}$ increases monotonically as a function of mass for all redshift bins. This result strongly supports the well established trend that more massive galaxies are more likely to be quenched. In addition, $f_{\rm{Q}}$ increases as redshift decreases at all masses and in both environments, suggesting that over cosmic time an increasing portion of galaxies have ceased their star-formation and have become quiescent galaxies.

While both high and low density environment $f_{\rm{Q}}$ exhibit a similar mass dependence and increase over cosmic time, for each redshift bin there is a significant difference where $f_{\rm{Q}}(\mathcal{M})$ in high density environments is greater than $f_{\rm{Q}}(\mathcal{M})$. In other words, galaxies in high density environments are more likely to be quenched than galaxies in low density environments.This reflects the long observed morphology-density relation (\cite{dresseler84a}; \cite{desai07a}) as well as the color-density relation (citation). In addition, our $f_{Q}$ evolution over cosmic time also agrees with recent measurements of SFR evolution over cosmic time in \cite{Alberts:2014aa} and the SSFR-density relation in \cite{cooper08a}.

Although a clear comparison between redshift bins is limited due to the stellar mass completeness limits, Figure \ref{fig:qf} illustrates a slight mass dependence in the $f_{\rm{Q}}$ evolution. $f_{\rm{Q}}$ in low density environments shows a greater evolution between redshift bins at high masses than at low masses. In contrast, the $f_{\rm{Q}}$ in high density environments shows a greater evolution between redshift bins at low masses than at high masses.

Furthermore, the results are also consistent with previous measurements of the quiescent fraction. Using a group-finding algorithm on the SDSS DR7 catalog, \cite{Tinker:2011aa} presented the relationship between $f_{\rm{Q}}$ and overdensity for galaxies within the mass range $\rm{log} \; \mathcal{M}_{*} = [9.8, 10.1]$. The \cite{Tinker:2011aa} $f_{\rm{Q}}$ values at the lowest and highest overdensities, $f_{\rm{Q}} \sim 0.4, \sim 0.6$ respectively, are consistent with our SDSS low and high density environment $f_{\rm{Q}}$ at the lowest mass bin $\rm{log} \; \mathcal{M}_{*} \sim 10.2$. Likewise at higher redshifts, our high and low environment $f_{\rm{Q}}$ results are in general agreement with the $F_{\rm{blue}}$ values for group and isolated galaxies from the zCOSMOS Redshift Survey, as presented in \cite{Iovino:2010aa}. \cite{Iovino:2010aa} constructs a mass complete sample of isolated galaxies and group galaxies from the \cite{Knobel:2009aa} Group Catalog and compares $F_{\rm{blue}}$ for the two environments.

@@
